Adopting agile in the large: motivations, success factors and challenges

### 2014-05-14 journal/article.tex
Editing

% Change resistance
% Lack of investment in transformation
% Agile is found to be hard
% Large organization issues
% Coordinating work between many teams
% Integrating other functions than development to agile
% Other challenges in transformation (zealots, falling back)

@@

The primary studies revealed challenges which relate particularly to large
scale. Additional layers of management are usually necessary to steer large
groups of people, but agile methods provide little guidance on how to organize
management. Also, as large organizations accomodate many development teams
problems with synchronizing the development models of teams may cause problems.

@@

The existence of additional management positions may be problematic with agile
processes as they emphasize self organization.
The role of middle management was seen as unclear in agile methods [P2]. This is
problematic as an agile transformation requires cultural change especially on
the middle management level [P2].
It was described that people in management positions needed to resist the
tendency to take command and control to allow room for self organization, but
the change in role was difficult to achieve for the people involved [P11, P52].
Nielsen and McMunn [P30] describe how the project management group had
previously worked through big up front plans and competing of resources, but
those ways would need to dramatically change.

@@

@@

In an enterprise setting quality assurance (QA) tasks will require effort beyond
the general agile convention of doing testing within a crossfunctional team. In
large development efforts the agile model may need to be extended to accomodate
additional testing [P31]. Organizations may have existing separate QA teams that
must be coordinated to work with development teams [P17, P30, P48]. Integrating
enterprise scale QA will pose some additional challenges to agile methods.

@@

% Lack of plans (a guess -- not included)?

@@

Another issue that should be avoided is overenthusiasm towards agile methods.
In several cases there was mentionings about change leaders or teams becoming
agile zealots. For instance, Evans describes how some members of the agile
community were becoming too evangelic, which made people take sides for or
against agile development [12]. In another case team members started out with an
overly eager attitude, but when agile did not deliver improvements the
interest faded and started to go back to the old process [P20]. Attempting to
implement agile too strictly may cause conflicts, and especially in a large
organization the change leaders need to maintain a collaborative attitude
towards various groups in the surrounding organization [P6]. Introducing agile
methods does not guarantee success, and therefore they should not be followed
blindly [P4].

% People do not speak their minds

In one case a passive-aggressive organization culture was described as a
challenge. Ranganath describes how people did not speak their minds in meetings,
thus creating a false sense of agreement when talking about how the organization
should develop. Because of this resistance and concerns were left growing, and
acted against achieving a successful transformation. To to avoid these issues
change leaders worked with team members on an individual level to win confidence 
and make their voices heard [P40].

In several cases challenges in the transformation resulted in people falling
back to the old model of working.
In some cases it was only a struggle to learn agile practices, but in other
cases the old model displaced agile.
Development work has to go on during the transformation but there will be new
things to learn for the team. Stress caused by the combination of schedule
pressure and much change at once will pull people back to the old way of working
[P11, P18, P38].
Schatz and Abdelshafi tell how even subtle trouble may risk the transformation,
as people will always look for reasons to revert to familiar behavior [P44].
Teams without adequate training were struggling with applying agile practices
correctly, and the challenge the new practices posed made people to abandon them
and return to the ways they know [P6, P49].

In some cases agile was seen as an overhead, and was therefore abandoned. For
instance, as new practices were being introduced there was a decrease
performance, and when teams realized that the benefits are not immediate they
started reverting to the old model [P21].

When a release schedule with fixed deadlines that business required was combined
to agile managers started to behave authoritatively and the self organization of
agile started to break down [P31]. % (Skeptics used this as a sign of that agile can not work)

In one case new senior appointments were changed the management to be less
favorable towards agile, and a waterfall development model started to return
[P12].

% Include quotation?
% * Some teams mirrored waterfall approaches in their behavior --> Did not work
% [P32]
% Then comes execution and the learning really begins. Teams’ working habits
% determine their success.  Often teams quickly ignore plans in favor of using
% tactical approaches that mirror waterfall thinking. This contrasts nicely with
% those more attuned to applying agile.

>>>>

% Change resistance
% Lack of investment in transformation
% Agile is found to be hard
% Large organization issues
% Coordinating work between many teams
% Integrating other functions than development to agile
% Integrating requirements management and quality assurance
% Other challenges in transformation (zealots, falling back)

@@

The primary studies revealed challenges which relate particularly to large
scale. Additional layers of management are usually necessary to steer large
groups of people, but agile methods provide little guidance on how to organize
management. Also, as large organizations accomodate many development teams there
may be problems if the development models between teams are not synchronized.
Internal fragmenttation is a further problem that may be encountered in large
organizations.

@@

The existence of additional management positions may pose problems to agile
processes that emphasize self organization.
The role of middle management was seen as unclear in agile methods [P2]. This is
problematic as an agile transformation requires cultural change especially on
the middle management level [P2].
It was described that people in management positions needed to resist the
tendency to take command and control to allow room for self organization, but
the change in role was difficult to achieve for the people involved [P11, P52].
Nielsen and McMunn [P30] describe how the project management group had
previously worked through big up front plans and competing of resources, but
those ways would need to dramatically change.

@@

\subsubsection{Integrating requirements management and quality assurance}

Traditionally development is preceeded by requirements engineering and succeeded
by quality assurance (QA) activities. Agile methods suggest that essential parts
of these activities would be performed within the development team. The effort
required for managing requirements and QA for large systems may be too large for
individual teams to handle.

@@

In an enterprise setting quality assurance tasks will require effort beyond
the general agile convention of doing testing within a crossfunctional team. In
large development efforts the agile model may need to be extended to accomodate
additional testing [P31]. Organizations may have existing separate QA teams that
must be coordinated to work with development teams [P17, P30, P48]. Integrating
enterprise scale QA will pose some additional challenges to agile methods.

@@

There were still some other challenges in the transformation that do not fit in
the categories presented above. Two particular problems are worth mentioning.
Firstly, there were certain factors that pulled people back to the old ways of
working, and secondly, excessive enthusiasm in agile had negative effects.

In several cases challenges in the transformation resulted in people falling
back to the old model of working. In some cases it was only a temporary struggle
while learning agile practices, but in other cases the old model displaced
agile.
Development work has to go on during the transformation but there will be new
things to learn for the team. Stress caused by the combination of schedule
pressure and much change at once will pull people back to the old way of working
[P11, P18, P38].
Schatz and Abdelshafi tell how even subtle trouble may risk the transformation,
as people will always look for reasons to revert to familiar behavior [P44].
Teams without adequate training were struggling with applying agile practices
correctly, and the challenge the new practices posed made people to abandon them
and return to the ways they know [P6, P49].

In some cases agile was seen as an overhead, and was therefore abandoned. For
instance, as new practices were being introduced there was a decrease
performance, and when teams realized that the benefits are not immediate they
started reverting to the old model [P21].
Evans [P12] describes that new senior appointments changed the management to be
less favorable towards agile, and a waterfall development model started to
return.

@@

A phenomena that troubled some organizations was overenthusiasm towards agile
methods. In several cases there was mentionings about change leaders or teams
becoming agile zealots. For instance, Evans [12] describes how some members of
the agile community were becoming too evangelic, which made people take sides
for or against agile development. In another case team members started out with
an overly eager attitude, but when agile did not deliver improvements the
interest faded and started to go back to the old process [P20]. Attempting to
implement agile too strictly may cause conflicts, and especially in a large
organization the change leaders need to maintain a collaborative attitude
towards various groups in the surrounding organization [P6]. Introducing agile
methods does not guarantee success, and therefore they should not be followed
blindly [P4].

% When a release schedule with fixed deadlines that business required was combined
% to agile managers started to behave authoritatively and the self organization of
% agile started to break down [P31]. % (Skeptics used this as a sign of that agile can not work)

% This??
% % People do not speak their minds
% In one case a passive-aggressive organization culture was described as a
% challenge. Ranganath describes how people did not speak their minds in meetings,
% thus creating a false sense of agreement when talking about how the organization
% should develop. Because of this resistance and concerns were left growing, and
% acted against achieving a successful transformation. To to avoid these issues
% change leaders worked with team members on an individual level to win confidence 
% and make their voices heard [P40].
